% ============================================================
% English Abstract
% ============================================================

As the global electronics industry advances toward deep integration and refined supply chain management, electronic component selection has become a labor-intensive and risk-concentrated bottleneck in hardware development lifecycles. Traditional manual workflows require engineers to verify multi-dimensional constraints—input/output voltage range, maximum output current, temperature rating, package constraints, inventory levels, and lifecycle status—across thousands of part numbers from dozens of manufacturers, typically consuming over two hours per design, with no systematic supply chain risk identification or standardized engineering documentation output.

This paper presents an intelligent component selection and risk assessment Agent system for the eZ-PLM electronic component management platform. The system is built upon a five-stage linear pipeline architecture—natural language requirement parsing, real-time API component retrieval, hybrid intelligent scoring, evidence chain construction, and standardized report generation—enabling end-to-end selection automation through the coordinated operation of a deterministic rule engine and a large language model (LLM) inference layer.

The primary technical contributions are as follows:

\textbf{(1) Manufacturer-prefix grouped query strategy for EZ-PLM API coverage.} Since the eZ-PLM API only supports MPN-prefix keyword search, a category/topology-to-manufacturer-prefix mapping strategy is proposed, aggregating part number prefixes of four open manufacturers (TI, ADI including LTC, Microchip, and ST) to achieve recall of over 200 active components per query, compensating for the platform's lack of semantic search capability.

\textbf{(2) Four-level fault-tolerant requirement parsing chain.} A cascaded parsing strategy is designed: LLM semantic parsing, rule-based category/topology override, voltage-comparison topology fallback ($V_{in} > V_{out}$ forces buck; $V_{in} < V_{out}$ forces boost), and temperature-range regex matching. This resolves common engineering parsing defects including milliampere unit mismatches, negation pattern failures (``非车规'' $\rightarrow$ industrial grade), and LLM hallucination misclassifying buck converters as LDO regulators.

\textbf{(3) Reference-design-grounded LLM soft scoring.} An LLM scoring mechanism grounded by eZ-PLM reference design API data is introduced. Actual reference designs serve as context to constrain LLM inference, yielding a four-dimensional hybrid score: parameter matching (40\%), supply chain stability (10\%), application fitness (25\%), and design maturity (25\%). When no reference design data is available, the system automatically degrades to a rule-only two-dimensional score (parameter 80\% + supply chain 20\%).

\textbf{(4) Dual-layer risk assessment with data provenance.} A risk report architecture separating rule-engine fact verification from LLM engineering narration is implemented. The rule layer detects objective risks—supplier concentration, zero inventory, obsolete lifecycle, missing data fields—using deterministic logic. The LLM layer is restricted to providing engineering context for pre-verified risk items only, with each narrative section explicitly labeled by data source to guarantee the rigor and traceability of risk reports.

\textbf{(5) Standardized intermediate representations for eZ-PLM interoperability.} PartIR (21 fields), ScoreBreakdown (including scoring mode and LLM sub-scores), TopologyIR (four sub-models: topology node graph, external component parameters, thermal performance estimation, and PCB layout rules), and RiskIR (with FMEA quantification fields) are defined. Three engineering output documents—BOM selection list, supply chain risk assessment report, and circuit topology analysis report—are produced in formats ready for engineering review and eZ-PLM platform integration.

Experimental validation demonstrates 100\% pass rate across ten DC-DC buck converter selection test cases. In the eZ-PLM real-time API integration test, a ``12\,V to 5\,V / 3\,A industrial-grade'' query successfully returned 31 active TI components (TPS54xxx/LM2596x series), with the top-ranked device scoring 76.67 (rule-only mode). All three engineering output documents were fully generated under realistic requirements; the topology analysis report includes quantitative L/C value calculations derived from switching frequency and ripple current constraints, as well as thermal margin assessment. A RAG engineering knowledge module and a multi-turn interactive Agent mode are currently under iterative development.
